### 2017-11-30 Docs/Thesis/docs/chapter4.tex
update thesis text

%2nd-review
Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood. Some observations must be made. Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero. To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively. We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{\textcolor{red}{github-link-aqui}}

>>>>

%2nd-review
Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood. Some observations must be made. Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero. To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively. We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests/PrototypeDataProcessor}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests/PrototypeDataProcessor}}

### 2017-11-30 Docs/Thesis/docs/chapter6.tex
update thesis text

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1   & Optimizing linear regression                      &                                & \textcolor{red}{high} \\
		2   & Flow-merging option                               &                                & medium \\
		3   & Smart flow-scheduler                              &                                & \textit{high} \\
		4   & \texttt{DataProcessor::minimumAmountOfPackets}    &                                & low \\
		5   & DPDK KNI interfaces                               &                                & medium \\
		6   & Multi-thread C++ sniffer                          &                                & \textit{high} \\ \hline
		7   & Cluster operation (high speed traffic-gen) & \multirow{-7}{*}{Performance}  & \textit{high} \\
		8   & Model inter-packet times on \texttt{TinsFlow}     &                                & \textit{high} \\
		9   & D-ITG flow generator (\texttt{DitgFlow})          &                                & low \\
		10  & DPDK flow generator (\texttt{DpdkFlow})           &                                & medium \\
		11  & Ostinato flow generator (\texttt{OstinatoFlow})   & \multirow{-4}{*}{Tool support} & low \\ \hline
		12  & \texttt{DataProcessor::min\_time}                 &                                & low \\
		13  & \texttt{DataProcessor::m\_min\_on\_time}          &                                & low \\
		14  & \texttt{DataProcessor::m\_session\_cut\_time}     &                                & low \\
		15  & Minimum number of packets per flow option         & \multirow{-4}{*}{Calibration}  & low \\ \hline
		16  & Python API/Lua for traffic generation             &                                & low \\
		17  & Crafter of  pcap files                            & \multirow{-2}{*}{New features} & low \\

@@

(1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor. The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows. The time expended for processing traces, in this case, is exceeding tens of hours. In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations. Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance.

@@

(3) Currently, all the flow threads are instantiated once the traffic generations start. A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows. For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth.

(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. If it is smaller, SIMITAR just uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is poor . Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve a more reasonable performance for individual flows, and reduce the processing time.

@@

After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype. In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory. Again, we planned a methodology, procedure, and validate these ideas, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?" (in the appendix ~\ref{ap:publications}). Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements. In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library. Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}. This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.

@@

Finally, we created a list of improvements and future works, aiming the improvement of performance on processing time, and packet generation; and the methods to improve the realism of the traffic generated. In the is we believe to overcome the current limitations.

>>>>

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1   & Optimizing linear regression                       &                                & \textbf{\textit{high}} \\
		2   & Flow-merging option                                &                                & \textit{medium} \\
		3   & Smart flow-scheduler and thread/process management &                                & \textbf{\textit{high}} \\
		4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
		5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
		6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
		7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
		8   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
		9   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
		10  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
		11  & Ostinato flow generator (\texttt{OstinatoFlow})    & \multirow{-4}{*}{Tool support} & low \\ \hline
		12  & \texttt{DataProcessor::min\_time}                  &                                & low \\
		13  & \texttt{DataProcessor::m\_min\_on\_time}           &                                & low \\
		14  & \texttt{DataProcessor::m\_session\_cut\_time}      &                                & low \\
		15  & Minimum number of packets per flow option          & \multirow{-4}{*}{Calibration}  & low \\ \hline
		16  & Python API/Lua for traffic generation              &                                & low \\
		17  & Crafter of  pcap files                             & \multirow{-2}{*}{New features} & low \\

@@

(1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor. The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows. The time expended for processing traces, in this case, is exceeding tens of hours. In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations. Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance, along with some code optimizations.

@@

(3) Currently, all the flow threads are instantiated once the traffic generations start. A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows. For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth. Another improvement in traffic generations is reduced memory consumption per thread and process, and optimize the code.

(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. If it is smaller, SIMITAR just uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is poor. Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve a more reasonable performance for individual flows, and reduce the processing time.

@@

After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype. In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory. Again, we planned a methodology, procedure, and validate these ideas, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?" (in the appendix ~\ref{ap:publications}). Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements. In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library. Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}. This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.

@@

Finally, we created a list of improvements and future works, aiming the improvement of the software, inclusing, performance better processing time and packet generation, and the realismo on the traffic generated. In fact, the greater bootleneck of the project resides on processing performance. The results on realism, even with a lot of room for improovments, already have a good quality. With the proposed future works we believe to be possible overcome the current limitations.
